Word learning at the semantics pragmatics interface

### 2020-04-10 paper/bda_fig.tex
a few more versions of the bda model

\begin{figure}[ht]
\begin{center}
\begin{tabular}{cc}
\begin{tikzpicture}
	%% RSA nodes and data
	\node[obs](data_comb){$d^{CM}_{i, j, k}$};
	\node[obs, left=3 of data_comb, yshift=3cm](data_me){$d^{ME}_{i, j}$};
	\node[obs, right=2 of data_comb, yshift=1cm](data_cg){$d^{CG}_{i}$};

	\node[det, above=of data_me](L1_me){$L'_1$};
	\node[det, above=of data_comb](L1_comb){$L_1$};

	\edge{L1_me}{data_me};
	\edge{L1_comb}{data_comb};

	% COMMON GROUND
	\node[latent, above=of data_cg](rho){$\rho_i$};
	\node[latent, above=of rho, xshift=-0.5cm](beta_rho_int){$\beta^{\rho}_0$};
	\node[latent, above=of rho, xshift=0.5cm](beta_rho_slope){$\beta^{\rho}_1$};

@@

	\node[latent, above=of L1_me](alpha){$\alpha_i$};
	\node[latent, above=of alpha, xshift=-0.5cm](beta_alpha_int){$\beta^{\alpha}_0$};
	\node[latent, above=of alpha, xshift=0.5cm](beta_alpha_slope){$\beta^{\alpha}_1$};

	\edge{alpha}{L1_me};
	\edge{beta_alpha_int}{alpha};
	\edge{beta_alpha_slope}{alpha};
	\edge{alpha}{L1_comb};

@@

	\plate{plate_data_me}{
		(data_me)
	}{$i \in \mathcal{P}_{1}$}

	\plate{plate_data_comb}{
		(data_comb)
	}{$i \in \mathcal{P}_{3}$}

	\plate{plate_data_cg}{
		(data_cg)
	}{$i \in \mathcal{P}_{2}$}

	\plate{plate_condition}{(plate_data_comb)}{$k \in \mathcal{K}$};

	\plate{plate_items}{
		(plate_data_me)
		(plate_data_comb)
		(plate_condition)
		(L1_me)
		(L1_comb)
		(theta)
		(beta_theta_int)
		(beta_theta_slope)
	}{$j \in \mathcal{J}$}

>>>>

\begin{figure}[ht]
\begin{center}
\begin{tabular}{cc}
\begin{tikzpicture}
	%% RSA nodes and data
	\node[obs](data_comb){$d^{CM}_{{i}, j, k}$};
	\node[obs, xshift=-3cm, yshift=0cm](data_me){$d^{ME}_{{i}, j}$};
	\node[obs, xshift=3cm,  yshift=0cm](data_cg){$d^{CG}_{i}$};

	\node[det, above=of data_me](L1_me){$L'_1$};
	\node[det, above=of data_comb](L1_comb){$L_1$};
	\node[det, above=of L1_comb, xshift=-1.5cm, yshift=-0.5cm](RSA){$RSA$};

	\edge{L1_me}{data_me};
	\edge{L1_comb}{data_comb};
	\edge{RSA}{L1_me};
	\edge{RSA}{L1_comb};

	% COMMON GROUND
	\node[latent, above=of data_cg, yshift=0.1cm](rho){$\rho_i$};
	\node[latent, right=of rho, yshift=0.5cm](beta_rho_int){$\beta^{\rho}_0$};
	\node[latent, right=of rho, yshift=-0.5cm](beta_rho_slope){$\beta^{\rho}_1$};

@@

	\node[latent, left=of RSA, xshift=-1cm](alpha){$\alpha_i$};
	\node[latent, left=of alpha, yshift=0.5cm](beta_alpha_int){$\beta^{\alpha}_0$};
	\node[latent, left=of alpha, yshift=-0.5cm](beta_alpha_slope){$\beta^{\alpha}_1$};

%	\edge{alpha}{L1_me};
	\edge{beta_alpha_int}{alpha};
	\edge{beta_alpha_slope}{alpha};
	\edge{alpha}{RSA};

	\node[latent, above=of RSA, yshift=-0.25cm](theta){$\theta_{ij}$};
	\node[latent, above=of theta, xshift=-1.25cm, yshift=-0.5cm](beta_theta_int){$\beta^{\theta}_{0, j}$};
	\node[latent, above=of theta, xshift=1.25cm, yshift=-0.5cm](beta_theta_slope){$\beta^{\theta}_{1, j}$};

	\edge{theta}{RSA};
%	\edge{theta}{L1_comb};
	\edge{beta_theta_int}{theta};
	\edge{beta_theta_slope}{theta};
	\edge{mu_theta_int}{beta_theta_int};
	\edge{sigma_theta_int}{beta_theta_int};
	\edge{mu_theta_slope}{beta_theta_slope};
	\edge{sigma_theta_slope}{beta_theta_slope};

%	\plate{plate_data_me}{
%		(data_me)
%	}{$i \in \mathcal{P}_{1}$}

%	\plate{plate_data_cg}{
%		(data_cg)
%	}{$i \in \mathcal{P}_{2}$}

	\plate{plate_condition}{(data_comb)(L1_comb)}{$k \in \text{expt.~conditions}$};

	\plate{plate_items}{
%		(plate_data_me)
%		(plate_data_comb)
%		(plate_condition)
	(plate_condition)
		(data_comb)
		(data_me)
		(L1_me)
		(L1_comb)
		(theta)
		(beta_theta_int)
		(beta_theta_slope)
	}{$j \in \text{items}$}

	\plate{plate_data_comb}{
		(data_comb)
		(data_cg)
		(data_me)
		(plate_condition)
		(rho)
		(theta)
		(alpha)
		(L1_me)
		(L1_comb)
%		(plate_items)
	}{$i \in \text{2-to-4 year olds}$}

\begin{figure}[ht]
\begin{center}
\begin{tabular}{cc}
\begin{tikzpicture}
	%% RSA nodes and data
	\node[obs](data_comb){$d^{CM}_{i, j, k}$};
	\node[det, above=of data_comb](L1_comb){$L_1$};
	\edge{L1_comb}{data_comb};

%	\node[det, right=of data_me](L1_me){$L'_1$};

%	\edge{L1_me}{data_me};

	% COMMON GROUND
	\node[latent, right=of L1_comb](rho){$\rho_i$};
	\node[obs, right=of rho](data_cg){$d^{CG}_{i}$};
	\node[latent, right=of rho, yshift=-2cm](beta_rho_int){$\beta^{\rho}_0$};
	\node[latent, right=of rho, yshift=-3cm](beta_rho_slope){$\beta^{\rho}_1$};

	\node[latent, left=of L1_comb](alpha){$\alpha_i$};
	\node[latent, left=of alpha, yshift=-2cm](beta_alpha_int){$\beta^{\alpha}_0$};
	\node[latent, left=of alpha, yshift=-3cm](beta_alpha_slope){$\beta^{\alpha}_1$};
	\node[det, left=of alpha](L1_me){$L'_1$};
	\node[obs, left=of L1_me](data_me){$d^{ME}_{i, j}$};

	\edge{alpha}{L1_me};
	\edge{beta_alpha_int}{alpha};
	\edge{beta_alpha_slope}{alpha};
	\edge{alpha}{L1_comb};
	\edge{L1_me}{data_me};

@@

		\plate{plate_items_me}{
		(data_me)
	}{$j \in \text{items}$}

	\plate{plate_data_me}{
		(data_me)
		(L1_me)
		(alpha)
		(plate_items_me)
	}{$i \in \mathcal{P}_{1}$}

	\plate{plate_data_cg}{
		(data_cg)(rho)
	}{$i \in \mathcal{P}_{2}$}

	\plate{plate_items}{
		(data_comb)(L1_comb)(theta)
	}{$j \in \text{items}$}

	\plate{plate_data_comb}{
		(data_comb)(rho)(alpha)(theta)(plate_items)
	}{$i \in \mathcal{P}_{2}$}

\begin{figure}[ht]
\begin{center}
\begin{tabular}{cc}
\begin{tikzpicture}
	%% RSA nodes and data
	\node[obs](data_comb){$d^{CM}_{i, j, k}$};
	\node[det, above=of data_comb](L1_comb){$L_1$};
	\edge{L1_comb}{data_comb};

%	\node[det, right=of data_me](L1_me){$L'_1$};

%	\edge{L1_me}{data_me};

	% COMMON GROUND
	\node[latent, right=of L1_comb](rho){$\rho_i$};
	\node[obs, right=of rho](data_cg){$d^{CG}_{i}$};
	\node[latent, right=of rho, yshift=-2cm](beta_rho_int){$\beta^{\rho}_0$};
	\node[latent, right=of rho, yshift=-3cm](beta_rho_slope){$\beta^{\rho}_1$};

	\node[latent, left=of L1_comb, yshift=0.5cm](alpha){$\alpha_i$};
	\node[latent, left=of alpha, yshift=-2cm](beta_alpha_int){$\beta^{\alpha}_0$};
	\node[latent, left=of alpha, yshift=-3cm](beta_alpha_slope){$\beta^{\alpha}_1$};
	\node[det, left=of alpha, yshift=1.8cm](L1_me){$L'_1$};
	\node[obs, left=of L1_me](data_me){$d^{ME}_{i, j}$};

	\edge{alpha}{L1_me};
	\edge{beta_alpha_int}{alpha};
	\edge{beta_alpha_slope}{alpha};
	\edge{alpha}{L1_comb};
	\edge{L1_me}{data_me};

	{
	\tikzset{plate caption/.append style={below right=2pt and 0pt of #1.south west}}
		\plate{plate_items_me}{
			(data_me)(L1_me)(theta)(beta_theta_int)(beta_theta_slope)
		}{$j \in \text{items}$}	
	}

	{
	\tikzset{plate caption/.append style={below right=0pt and 0pt of #1.south west}}
	\plate{plate_data_me}{
		(data_me)
		(L1_me)
		(alpha)
%		(plate_items_me)
	}{$i \in \mathcal{P}_{1}$}
	}

	\plate{plate_data_cg}{
		(data_cg)(rho)
	}{$i \in \mathcal{P}_{2}$}

	\plate{plate_items}{
		(data_comb)(L1_comb)(theta)
	}{$j \in \text{items}$}

	\plate{plate_data_comb}{
		(data_comb)(rho)(alpha)(theta)(plate_items)
	}{$i \in \mathcal{P}_{3}$}
